---
title: "P8105 - Homework 6"
author: "Mingkuan Xu"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,message=FALSE}
library(tidyverse)
library(corrplot)
library(modelr)
library(mgcv)
```

## Problem 1

### Part 1 - Data Preprocessing 

```{r message=FALSE}

birth_data = read_csv("birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    # parents' race, babysex and malform should be factored
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    babysex = as.factor(babysex),
    malform = as.factor(malform))

# Calculate number of missing values
sum(is.na(birth_data))
```
### Part 2 - Build Model

To build a regression model for the birth weight, we start by taking a closer look of each variables, calculate the pairwise correlations between variables, and list all the correlations between the birth weight and all other variables.
Notice that for columns pnumlbw and pnumgsa, all values are zero so we remove them. 

```{r}
birth_data_cor = birth_data %>%
  select(-babysex,-frace,-mrace,-malform,-pnumlbw,-pnumsga) %>%
  relocate(bwt) %>%
  cor(use="complete.obs")
corrplot(birth_data_cor, type = "upper", diag = FALSE)
```

Now we observe from the heatmap that bwt is associated with bhead, blength, delwt, and gaweeks, we consider building a simple regression model using these variables.

```{r}
model = lm(bwt ~ bhead + blength + delwt + gaweeks, data = birth_data)
summary(model)

birth_data %>%
  modelr::add_residuals(model) %>% 
  modelr::add_predictions(model) %>%
  ggplot(aes(x = pred, y = resid)) + 
  labs(
    x = "Predicted Values",
    y = "Residuals"
  ) + 
  geom_point() +
  theme_classic()
```

### Part 3 - Compare With Other Models

```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = birth_data)
summary(model_1)

model_2 = lm(bwt ~ bhead + blength + babysex + 
               bhead*blength + bhead * babysex + blength*babysex +
               bhead*blength*babysex,
             data = birth_data)
summary(model_2)

cv_df = crossv_mc(birth_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    model_0  = map(train, ~lm(bwt ~ bhead + blength + delwt + gaweeks, data = .)),
    model_1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .)),
    model_2  = map(train, ~lm(bwt ~ bhead + blength + babysex + 
               bhead*blength + bhead * babysex + blength*babysex +
               bhead*blength*babysex,
             data = birth_data))) %>% 
  mutate(
    rmse_model_0 = map2_dbl(model_0, test, ~rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with('rmse')) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>%
  mutate(model = fct_inorder(model)) 

ggplot(cv_df,aes(x = model, y = rmse, fill = model, color = model)) + 
    geom_violin() +
    theme_minimal()

```

From the violin plot shown above, we can conclude the model fitted using head circumference, length, sex, and all interactions (including the three-way interaction) is the best, since it has the smallest rmse value; the model fitting using length at birth and gestational age is the worst,since it has the biggest rmse value.

## Problem 2

### Part 1 - Load Data

```{r message=FALSE,warning=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Part 2 - Bootstrap 

```{r}
weather_bootstrap = weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    r_square = map(models, broom::glance))

weather_bootstrap_rsquare =  weather_bootstrap %>% 
#  select(results, r_square) %>%
#  unnest(results, r_square)
  unnest(r_square) %>% 
  select(r.squared)

ggplot(weather_bootstrap_rsquare,aes(x = r.squared)) + 
  geom_density() + theme_classic()

weather_bootstrap_rsquare %>%
  summarise("Lower CI" = quantile(r.squared, probs = 0.025),
            "Upper CI" = quantile(r.squared, probs = 0.975)) %>% 
  knitr::kable(digits = 3)

weather_bootstrap_logbeta = weather_bootstrap %>% 
  unnest(results) 
```